### 2017-01-23 doc/manuscript.Rmd
First (rough) draft of discussion - conclusion

>>>>

## Final conclusion

In conclusion, we found that a TAGFA composition indicative of higher DNL
(containing higher 14:0, 14:1n-7, 16:0, and 16:1n-7) associated strongly lower
insulin sensitivity and moderately with lower beta-cell function. The fatty
acids that clustered together represent fatty acids created from DNL, which is
characteristic of higher simple carbohydrate (e.g. added sugar) intake. Our
results, which are congruent with current evidence, suggest that higher DNL
likely due to greater intake of simple or refined carbohydrates may increase the
risk of diabetes through worsening of insulin sensitivity.
